%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{times}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Yifan Zhang}} & Email : \href{mailto:yifaz41@uci.edu}{yifaz41@uci.edu}\\
  {Department of Computer Science, University of California-Irvine, CA 92612} & Mobile : 1(949)6640652 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California,\ Irvine\ (UCI)}{Irvine,\ CA}
      {Master of Computer Science}{Sep. 2018 -- Dec. 2019(expected)}
    \resumeSubheading
      {University of Electronic Science and Technology of China\ (UESTC)}{Chengdu,\ CHINA}
      {Bachelor of Engineering in Electrical Engineering\ \ \ \ \ \   GPA: \rm{3.71/4.00} }{Sep. 2014 -- Jun. 2018}
      \resumeSubheading
      {National Taiwan University of Science and Technology\ (NTUST)}{Taipei,\ TAIWAN}
      {Exchange student in Electronic Engineering \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  GPA: \rm{4.15/4.30} }{Sep. 2016 -- Feb. 2017}
  \resumeSubHeadingListEnd


%-----------SKILLS-----------------
\section{\textbf{Skills}}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{\hspace{50}Java, C++, Python, SQL, JavaScript, LaTex}
    \resumeSubItem{Tools}{\hspace{144}Intellij IDEA, Linux, Putty, Sublime Text, HTML, Visual Studio Code}
    
  \resumeSubHeadingListEnd

%-----------Intern-----------------
\section{\textbf{Working Experience}}
\resumeSubHeadingListStart

    \resumeSubheading
      {Chicago Summer Internship Program,\ Ignite}{Chicago,\ IL}
      {Assistant programmer}{Jul. 2016 - Aug. 2016}
      \resumeItemListStart
        \item
          {Partook in the development of crawler software and improvement of its algorithm to extract information of companies (emails, phone number etc.) into Excel}
        \item
          {Proved a valuable team member by good communication and work efficiency in a network consultancy agency }
      \resumeItemListEnd
      
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{\textbf{Project Experience}}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Minesweeper AI Agent: An AI Coding Project,\ UCI}{Irvine,\ CA}
      {Team leader}{Sep. 2018 - Oct. 2018}
        \begin{itemize}
            \item Designed the whole framework of the project and the logic flow to maximize success rate of the agent
            \item Utilized heuristic estimation in order to find the unit which would most probably be a mine
            \item Succeed to complete 70\% of one thousand 16*16 worlds with 40 mines and 30\% of one thousand 16*30 worlds with 99 mines
        \end{itemize}

    \resumeSubheading
      {Research on License Plate Recognition Technology,\ UESTC}{Chengdu,\ CHINA}
      {Researcher}  {Dec. 2017 - May 2018}
      \begin{itemize}
        \item
          {Designed system for automatically recognizing car plates in different environments}
        \item
          {Used Binarization and Grayscale algorithm to preprocess images}
        \item
          {Combined Genetic Algorithm in order to detect the actual position of plates which optimized the accuracy of system}
        \item
          {Used template matching algorithm to cover most situations and implemented ANN to deal with other complicated situations}
      \end{itemize}
   

    \resumeSubheading
      {Autonomous Landing System of 4-axis Drone,\ NTUST}{Taipei,\ TAIWAN}
      {Researcher}{Sep. 2016 - Jan. 2017}
      \begin{itemize}
        \item Implemented Kalmen and particle control algorithm (predictive function) to achieve automated landing
         \item Involved in the testing and coding part and worked with master students to solve system crash problem by debugging code imcompatibility
      \end{itemize}
  
    \resumeSubHeadingListEnd






%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
